---
title: "Assignment2-Submission"
output: html_document
---
# Name: Sieun Bae
# ID: 2016310153

# 0 Ensure ggplot2 is loaded
```{r}
library(ggplot2)
```

# Q1a) Meaning of "?" in dataset:
# Answer: NA

```{r}
# Q1b) Read diabetes_readmit.csv into a data frame. Enter your code below
df <- read.csv("diabetes_readmit.csv", na.strings = "?")
```

# Q1c) What is the effect of using na.strings="?" in read.csv
# Answer: It replaces "?" string to NA, so it shows actual meaning of the data, and makes easier to handle it.

```{r}
# Q2a) Calculate the number of NAs in each column and sort them in decreasing order. Enter your code below.
sort(colSums(is.na(df)), decreasing = TRUE)
```
# column name with most NAs: weight
# column name with second most NAs: medical_specialty

##  Bonus
```{r}
# Q2a_bonus) Instead of just returning the number of NAs in the column, return the number of NAs as a proportion of the overall data.
sort(colSums(is.na(df))/nrow(df), decreasing = TRUE)
```


```{r}
# Q2b) Remove two columns with most NAs
df <- subset(df, select = -c(weight, medical_specialty))
```

# Q2c) Which other one or two column(s) you would choose to remove and why?
# Answer: The following columns which were sorted in decreasing order by the number of NAs are "race" and "diag_3". Because those two have more NA elements, they can be the candidates to be chosen. 
# However, "race" has 2273 NA elements which is just 2.2%, and "diag_3" has 1423 NA elements which is just 1.3% (occupy few part of total). So I would not remove any column right now. But if I face an unavoidable time to reduce the data size, I would choose race, then diag_3. 

```{r}
# Q3a) Convert readmitted to an ordered factor 
df$readmitted <- 
  factor(df$readmitted, levels = c("NO", "<30", ">30"), ordered=TRUE)
str(df$readmitted)
```

```{r}
# Q3b) Plot bar of age filled by readmitted
ggplot(df, aes(age, readmitted)) +
  geom_col()
```

# Q3c) The group with the highest readmission count:
# Answer: age "70-80" group has the highest readmission count

```{r}
# Q3d) Density plot of time in hospital 
ggplot(df, aes(time_in_hospital)) + 
  geom_density()
```

```{r}
# Q3e) Facet the density plot with age
ggplot(df, aes(time_in_hospital, fill=age)) + 
  geom_density() +
  facet_wrap(df$age)
```

```{r}
# Q3f) Adding gender in.
ggplot(df, aes(time_in_hospital, fill=gender)) + 
  geom_density() +
  facet_wrap(df$age)
```

```{r}
# Q3g) Replot without errorneous values "Unknown/Invalid"
ggplot(df[df$gender %in% c("Female", "Male"),], 
       aes(time_in_hospital, fill=gender)) +
  geom_density() +
  facet_wrap(df[df$gender %in% c("Female", "Male"),]$age)
```

```{r}
# Q3h) Smoother visualisation and labels
ggplot(df[df$gender %in% c("Female", "Male"),], 
       aes(time_in_hospital, fill=gender)) +
  geom_density(alpha = 0.5, adjust = 2) +
  facet_wrap(df[df$gender %in% c("Female", "Male"),]$age) +
  scale_fill_discrete("Gender") +
  ggtitle("Time Spent in Hospital by Age Group and Gender by Sieun Bae") +
  xlab("Time Spent in Hospital") +
  ylab("Density") 
```

```{r}
# Q3i) Save the last plot as a .jpg file.
  ggsave(filename = "SieunBae-2016310153-diabetes.jpg", width=7, height=5)
```

# Q3j) Graph interpretation:
# Answer: Older ppl spent more time in hospital. 














